---
title: "Supplementary file: Daily, prospective association of sleep, physical activity, and sedentary behaviour with affect: A Bayesian multilevel compositional data analysis "
author: "Flora Le (flora.le@monash.edu)"
# date: "`r Sys.Date()`"
output: 
  html_document:
    theme: spacelab
    highlight: zenburn
    toc: yes
    toc_float: yes
    collapsed: no
    smooth_scroll: no
    toc_depth: 4
    fig_width: 9
    fig_height: 4
    fig_caption: yes
    number_sections: false
---

This file presents the full 
results for 
**Daily, Prospective Association of Sleep, Physical Activity, and Sedentary Behaviour with Affect: A Bayesian Multilevel Compositional Data Analysis**.

```{r, echo=FALSE, message=FALSE}
source("24h-affect-supp.R")
```

# Main analysis

## Diagnostic statistics
### ${\hat{R}}$
```{r, echo=FALSE, message=FALSE}
kbl(rhat_summary, align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "transparent")
```

### Effective sample size (ESS)
#### Bulk ESS
```{r, echo=FALSE, message=FALSE}
kbl(ess_bulk_summary, align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "transparent") # #ADC7DA
```

#### Tail ESS
```{r, echo=FALSE, message=FALSE}
kbl(ess_tail_summary, align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "transparent") # #ADC7DA
```
### MCMC draw diagnostic plots
*Notes.* `b_bilr`s are coefficients for the between-person level effects of the 24h composition, 
while `b_wilr`s are within-person level effects. 

#### High arousal positive affect
```{r, echo=FALSE, message=FALSE, fig.height=8, fig.align='center'}
plot_mcmc_hapa[[1]]
```
```{r, echo=FALSE, message=FALSE, fig.height=7, fig.align='center'}
plot_mcmc_hapa[[2]]
```

#### Low arousal positive affect
```{r, echo=FALSE, message=FALSE, fig.height=8, fig.align='center'}
plot_mcmc_lapa[[1]]
```
```{r, echo=FALSE, message=FALSE, fig.height=7, fig.align='center'}
plot_mcmc_lapa[[2]]
```

#### High arousal negative affect
```{r, echo=FALSE, message=FALSE, fig.height=8, fig.align='center'}
plot_mcmc_hana[[1]]
```
```{r, echo=FALSE, message=FALSE, fig.height=7, fig.align='center'}
plot_mcmc_hana[[2]]
```

#### Low arousal negative affect
```{r, echo=FALSE, message=FALSE, fig.height=8, fig.align='center'}
plot_mcmc_lana[[1]]
```
```{r, echo=FALSE, message=FALSE, fig.height=7, fig.align='center'}
plot_mcmc_lana[[2]]
```

## Estimated difference for 30-minute pairwise reallocation between 24h behaviours
Models adjusted for age, sex, race/ethnicity, subjective social status, body mass index, alcohol use, smoking status, school status, work status, weekdays/weekend, daily wear time, and previous-day affect.

*Notes.* Statistical significance of individual parameters was set as Bayesian 95% posterior credible intervals (CIs) not including zero.

* MVPA = Moderate-to-Vigorous Physical Activity
* LPA = Light Physical Activity
* SB = Sedentary Behaviour

### High arousal positive affect
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sub_list[[1]][Level == "within"], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#FAF7F3")
```

### Low arousal positive affect
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sub_list[[2]][Level == "within"], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#EFE3E0")
```

### High arousal negative affect
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sub_list[[3]][Level == "within"], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#CFDAE2")
```

### Low arousal negative affect
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sub_list[[4]][Level == "within"], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#8399AE")
```

## Figures for within person level pairwise reallocation from 1 to 60 minutes

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
walk(h24_affect_plot_w, print)
```

# Sensitivity analysis
Models adjusted for weekdays/weekend, daily wear time, and previous-day affect.

### High arousal positive affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sen_sub_list[[1]][Level == "within"], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#FAF7F3")
```

### Low arousal positive affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sen_sub_list[[2]][Level == "within"], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#EFE3E0")
```

### High arousal negative affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sub_list[[3]][Level == "within"], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#CFDAE2")
```

### Low arousal negative affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sen_sub_list[[4]][Level == "within"], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#8399AE")
```

# Unadjusted analysis
Models not adjusted for covariates.

### High arousal positive affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_unadj_sub_list[[1]][Level == "within"], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#FAF7F3")
```

### Low arousal positive affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_unadj_sub_list[[2]][Level == "within"], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#EFE3E0")
```

### High arousal negative affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sub_list[[3]][Level == "within"], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#CFDAE2")
```

### Low arousal negative affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_unadj_sub_list[[4]][Level == "within"], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#8399AE")
```
