---
title: "Daily Reallocation of Movement Behaviours and Affect"
author: "Flora Le (flora.le@monash.edu)"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: spacelab
    highlight: zenburn
    toc: no
    toc_float: no
    collapsed: no
    smooth_scroll: no
    toc_depth: 4
    fig_width: 8
    fig_height: 4
    fig_caption: yes
    number_sections: true
---

This file presents the full 
daily reallocation of movement behaviours and affect
results using the
Bayesian compositional multilevel substitution analysis
for the manuscript:
**Daily Reallocation of Sleep, Physical Activity, and Sedentary Behaviour with Affect: A Bayesian Multilevel Compositional Data Analysis**.

*Notes.* 

* MVPA = Moderate-to-Vigorous Physical Activity
* LPA = Light Physical Activity
* SB = Sedentary Behaviour

```{r, echo=FALSE, message=FALSE}
source("24h-affect-results-setup.R")
```

# Statistics for 30-minute Reallocation

 * Reallocation of 30 minutes between movement behaviours and *high arousal positive affect*
 
```{r, warning=FALSE, echo=FALSE}
knitr::kable(h24_affect_sub_list[[1]])
```

 * Reallocation of 30 minutes between movement behaviours and *low arousal positive affect*
 
```{r, warning=FALSE, echo=FALSE}
knitr::kable(h24_affect_sub_list[[2]])
```

 * Reallocation of 30 minutes between movement behaviours and *high arousal negative affect*
 
```{r, warning=FALSE, echo=FALSE}
knitr::kable(h24_affect_sub_list[[3]])
```

 * Reallocation of 30 minutes between movement behaviours and *low arousal negative affect*
 
```{r, warning=FALSE, echo=FALSE}
knitr::kable(h24_affect_sub_list[[4]])
```

# Visualisation of Reallocation from 1 to 60 minutes of movement behaviours and affect
## Between person level

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
walk(h24_affect_plot_b, print)
```

## Within person level

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
walk(h24_affect_plot_w, print)
```
