---
title: "Supplementary data: Daily, prospective association of sleep, physical activity, and sedentary behaviour with affect: A Bayesian multilevel compositional data analysis "
author: "Flora Le (flora.le@monash.edu)"
# date: "`r Sys.Date()`"
output: 
  html_document:
    theme: spacelab
    highlight: zenburn
    toc: yes
    toc_float: yes
    collapsed: no
    smooth_scroll: no
    toc_depth: 4
    fig_width: 9
    fig_height: 4
    fig_caption: yes
    number_sections: false
---

This file presents the full 
results for 
**Daily, Prospective Association of Sleep, Physical Activity, and Sedentary Behaviour with Affect: A Bayesian Multilevel Compositional Data Analysis**.

*Notes.* Statistical significance of individual parameters was set as Bayesian 95% posterior credible intervals (CIs) not including zero.

* MVPA = Moderate-to-Vigorous Physical Activity
* LPA = Light Physical Activity
* SB = Sedentary Behaviour

```{r, echo=FALSE, message=FALSE}
source("24h-affect-supp.R")
```

## Estimated difference in for 30-minute reallocation between 24h behaviours
### High arousal positive affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sub_list[[1]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#FAF7F3")
```

### Low arousal positive affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sub_list[[2]], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#EFE3E0")
```

### High arousal negative affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sub_list[[3]], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#CFDAE2")
```

### Low arousal negative affect
 
```{r, warning=FALSE, echo=FALSE}
kbl(h24_affect_sub_list[[4]], espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#8399AE")
```

## Figures for reallocation from 1 to 60 minutes
### Between person level

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
walk(h24_affect_plot_b, print)
```

### Within person level

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
walk(h24_affect_plot_w, print)
```
